`r params$doc_title`

### 2022-12-20 scripts/MSc.Rmd
added wald estimates

@@

>>>>

# biology plausibility FTO & MC4R
# ## The mr_ivw function implements the inverse-variance method, informally 
# known as the "Toby Johnson" method. With a single genetic variant, this 
# is simply the ratio method.
fto_wald <- mr_wald_ratio(
  my_data_harm$beta.bmi[my_data_harm$SNP == "rs1558902"], 
  my_data_harm$beta.gsd[my_data_harm$SNP == "rs1558902"], 
  my_data_harm$se.bmi[my_data_harm$SNP == "rs1558902"], 
  my_data_harm$se.gsd[my_data_harm$SNP == "rs1558902"]
)
mc4r_wald <- mr_wald_ratio(
  my_data_harm$beta.bmi[my_data_harm$SNP == "rs6567160"], 
  my_data_harm$beta.gsd[my_data_harm$SNP == "rs6567160"], 
  my_data_harm$se.bmi[my_data_harm$SNP == "rs6567160"], 
  my_data_harm$se.gsd[my_data_harm$SNP == "rs6567160"]
)
# add rows
est.bmi.gsd <- est.bmi.gsd %>% 
  add_row(mr_methods = "FTO_Wald", estimate = fto_wald$b, se.estimate=fto_wald$se) %>% 
  add_row(mr_methods = "MC4R_Wald", estimate = mc4r_wald$b, se.estimate=mc4r_wald$se)

@@

# biology plausibility FTO & MC4R
# ## The mr_ivw function implements the inverse-variance method, informally 
# known as the "Toby Johnson" method. With a single genetic variant, this 
# is simply the ratio method.
fto_wald.gbc <- mr_wald_ratio(
  my_data_harm$beta.bmi[my_data_harm$SNP == "rs1558902"], 
  my_data_harm$beta.gbc[my_data_harm$SNP == "rs1558902"], 
  my_data_harm$se.bmi[my_data_harm$SNP == "rs1558902"], 
  my_data_harm$se.gbc[my_data_harm$SNP == "rs1558902"]
)
mc4r_wald.gbc <- mr_wald_ratio(
  my_data_harm$beta.bmi[my_data_harm$SNP == "rs6567160"], 
  my_data_harm$beta.gbc[my_data_harm$SNP == "rs6567160"], 
  my_data_harm$se.bmi[my_data_harm$SNP == "rs6567160"], 
  my_data_harm$se.gbc[my_data_harm$SNP == "rs6567160"]
)
# add rows
est <- est %>% 
  add_row(mr_methods = "FTO_Wald", estimate = fto_wald.gbc$b, se.estimate=fto_wald.gbc$se) %>% 
  add_row(mr_methods = "MC4R_Wald", estimate = mc4r_wald.gbc$b, se.estimate=mc4r_wald.gbc$se)
